---
title: "NES Insurance"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ANES Government Insurance

ANES VCF0806: There is much concern about the rapid rise in medical and hospital costs. Some (1988,1994-LATER: people) feel there should be a government insurance plan which would cover all medical and hospital expenses (1984 AND LATER: for everyone). (1996,2004: Suppose these people are at one end of a scale, at point 1). Others feel that (1988,1994-1996: all) medical expenses should be paid by individuals, and through private insurance (1984 AND LATER: plans) like Blue Cross (1984-1994: or [1996:some] other company paid plans). (1996,2004: Suppose these people are at the other end, at point 7. And of course, some people have opinions somewhere in between at points 2,3,4,5 or 6.) Where would you place yourself on this scale, or haven't you thought much about this?


```{r}
insure.df <- var_anes %>%
  select(year, insure) %>%
  filter(insure != 0, insure != 9)

insure.df$year <- factor(insure.df$year)
```


```{r}
# new data frame for crosstabs
insure_cross <- insure.df %>%
  filter(insure != 0, insure != 9) %>%
  na.omit() %>%
  group_by(year) %>%
  summarise(sum_all = sum(insure),
            sum_gov = sum(insure == 1, insure == 2, insure == 3),
            sum_between = sum(insure == 4),
            sum_private = sum(insure == 5, insure == 6, insure == 7)) %>%
  mutate(perc_gov = (sum_gov / sum_all * 100),
         perc_between = (sum_between / sum_all * 100),
         perc_private = (sum_private / sum_all * 100))

# round percentages to integers
insure_cross$perc_gov <- round(insure_cross$perc_gov, 0)
insure_cross$perc_between <- round(insure_cross$perc_between, 0)
insure_cross$perc_private <- round(insure_cross$perc_private, 0)

# reorder columns

insure_cross <- insure_cross[, c(1, 3, 6, 4, 7, 5, 8)]

kable(insure_cross,
      col.names = c("Year",
                "# Responses", 
                "% of total",
                "# of Responses",
                "% of total", 
                "# Responses", 
                "% of total")) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1, "Preference for Govt Insurance" = 2, "Between" = 2, "Preference for Private Insurance" = 2)) %>%
  column_spec(1, bold = T)
```


```{r}
insure_plot <- insure.df %>%
  select(year, insure) %>%
  filter(insure != 0, insure != 9) %>%
  group_by(year) %>%
  summarise(sum_all = sum(insure),
            sum_gov = sum(insure == 1, insure == 2, insure == 3), 
            sum_between = sum(insure == 4), 
            sum_private = sum(insure == 5, insure == 6, insure == 7)) %>%
  mutate(perc_gov = (sum_gov / sum_all),
         perc_between = (sum_between / sum_all),
         perc_private = (sum_private / sum_all))

ggplot(insure_plot, aes(x = factor(year), group = 1)) +
  geom_line(aes(y = perc_gov, color = "Preference for Govt Insurance")) +
  geom_line(aes(y = perc_between, color = "Between")) +
  geom_line(aes(y = perc_private, color = "Preference for Private Insurance")) +
  scale_y_continuous(label = scales::percent,
                     limits = c(0, 1)) +
  scale_x_discrete(expand = c(0.05, 0.05)) +
  scale_color_manual(name = '', values = c('Preference for Govt Insurance' = 'green3',
                                           'Between' = 'yellow',
                                           'Preference for Private Insurance' = 'deeppink3')) +
  labs(title = "Figure 3 \nGovt v Private Insurance Plans",
       x = "Year",
       y = "Percent of responses",
       caption = "Source: NES Cumulative Data File",
       color = NULL,
       group = NULL) +
  theme(plot.title = element_text(size = 15, face = "bold", vjust = 1, lineheight = 0.8, hjust = 0),
        axis.text.x = element_text(size = 10, hjust = 1, angle = 90),
        legend.position = "right",
        panel.background=element_rect(fill='grey96'),
        plot.margin = unit(c(3, 4, 3, 2), "mm"))
```


```{r}
# copy for code block
```
