---
title: "nes_clean"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Important variables

* weight variables
** VCF0009x/VCF0009y/VCF0009z

* demographics
** VCF0101 - age
** VCF0102 - age group
** VCF0104 - gender
** VCF0110 - education 4-cat
** VCF0114 - R family income group
** VCF0140 - education 6-cat
** VCF0105a - Race/ethnicity summary
** VCF0301 - Party Identification of Respondent
** VCF0302 - Initial Party ID response
** VCF0305 - strength of partisanship


* analysis
** VCF0201 - FT Democrats
** VCF0202 - FT Republicans
** VCF0203 - FT Protestants
** VCF0204 - FT Catholics
** VCF0205 - FT Jewish people
** VCF0206 - FT Black people
** VCF0207 - FT White people
** VCF0208 - FT Southerners
** VCF0211 - FT Liberals
** VCF0212 - FT Conservatives
** VCF0217 - FT Chicanos/Hispanics
** VCF0219 - FT Middle class people
** VCF0220 - FT People on welfare
** VCF0223 - FT Poor people
** VCF9006 - FT Women
** VCF0227 - Asian Americans
** VCF0233 - Illegal Aliens



```{r, echo=FALSE}
var_anes <- read_anes_cdf %>%
  select(
    year = VCF0004, id = VCF0006a,
    # weight variables
    weight1 = VCF0009x, weight2 = VCF0009y, weight3 = VCF0009z,
    # demographic variables
    age = VCF0101, age_group = VCF0102, gender = VCF0104, educ4 = VCF0110, fam_income = VCF0114, educ6 = VCF0140,
    # analysis variables
    gov_resp = VCF0805, insure = VCF0806, serve_spend = VCF0839)


# how do I remove the day and month?
# var_anes$year <- make_datetime(year = var_anes$year, month = FALSE, day = FALSE)
```